### 2009-10-15 doc/tech_doc/chelonia/arc-storage-documentation.tex
rename confusing configuration attribute in Shepherd's backend config (DataDir -> StoreDir)
please port to final

\begin{description}
    \item[ServiceID] is the ID of the service, currently it should be the URL of the service, because there is no information system where the services can be discovered by ID's.
    \item[CheckPeriod] specifies in seconds how frequently the Shepherd should check the existence and checksum of all the files on the storage node.
    \item[MinCheckInterval] specifies in seconds how much time the should Shepherd wait between two subsequent file checks. This ensures that the Shepherd does not use up all the resources of the hosting machine. After checking the checksum of a file, the Shepherd will always wait this long before checking the next file, even if this means that checking all the files takes longer than the `CheckPeriod' (in other words `MinCheckInterval' overrides `CheckPeriod' if the number of stored file is greater.)
    \item[CreatingTimeout] specifies in seconds the time before the Shepherd decides that a started file upload has failed. This is not fatal, if the file is uploaded eventually, it will be a valid replica, but after this much time the system starts creating new replicas just in case.
    \item[StoreClass] specifies which type of store the Shepherd should use for storing its metadata on disk (see Section \ref{sub:a_hash_configuration} for a list of choises).
    \item[StoreCfg] specifies configuration parameters for the store class. These parameters depends on the StoreClass, but will in most cases include \emph{DataDir}, i.e., the local directory to be used.
    \item[BackendClass] specifes which backend the Shepherd should use to communicate with the storage element service.
    \item[BackendCfg] specifies configuration parameters for the backend class: \textbf{DataDir} and \textbf{TransferDir} are the directories the backend will use (see Section~\ref{sub:shepherd_implementation}), \textbf{TURLPrefix} is the URL of the storage element service ending with a `/'.
    \item[LibrarianURL] is the URL of a Librarian where the Shepherd should send the reports about the health of the stored files.
    \item[BartenderURL] is the URL of a Bartender to which the Shepherd should connect if it wants to offer a replica for replication or recover a corrupted replica.
\end{description}

@@

\begin{verbatim}
    <Service name="pythonservice" id="shepherd">
        <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
        <ServiceID>https://localhost:60000/Shepherd</ServiceID>
        <CheckPeriod>20</CheckPeriod>
        <MinCheckInterval>0.1</MinCheckInterval>
        <CreatingTimeout>600</CreatingTimeout>
        <StoreClass>storage.store.cachedpicklestore.CachedPickleStore</StoreClass>
        <StoreCfg>
            <DataDir>./shepherd_data1</DataDir>
        </StoreCfg>
        <BackendClass>storage.shepherd.hardlinkingbackend.HopiBackend</BackendClass>
        <BackendCfg>
            <DataDir>./shepherd_store</DataDir>
            <TransferDir>./shepherd_transfer</TransferDir>
            <TURLPrefix>https://localhost:60000/hopi/</TURLPrefix>
        </BackendCfg>
        <LibrarianURL>https://localhost:60000/Librarian</LibrarianURL>
        <BartenderURL>https://localhost:60000/Bartender</BartenderURL>
        <ClientSSLConfig FromFile="clientsslconfig.xml"/>
    </Service>    
\end{verbatim}

>>>>

\begin{description}
    \item[ServiceID] is the ID of the service, currently it should be the URL of the service, because there is no information system where the services can be discovered by ID's.
    \item[CheckPeriod] specifies in seconds how frequently the Shepherd should check the existence and checksum of all the files on the storage node.
    \item[MinCheckInterval] specifies in seconds how much time the should Shepherd wait between two subsequent file checks. This ensures that the Shepherd does not use up all the resources of the hosting machine. After checking the checksum of a file, the Shepherd will always wait this long before checking the next file, even if this means that checking all the files takes longer than the `CheckPeriod' (in other words `MinCheckInterval' overrides `CheckPeriod' if the number of stored file is greater.)
    \item[CreatingTimeout] specifies in seconds the time before the Shepherd decides that a started file upload has failed. This is not fatal, if the file is uploaded eventually, it will be a valid replica, but after this much time the system starts creating new replicas just in case.
    \item[StoreClass] specifies which type of store the Shepherd should use for storing its metadata on disk (see Section \ref{sub:a_hash_configuration} for a list of choises).
    \item[StoreCfg] specifies configuration parameters for the store class. These parameters depends on the StoreClass, but will in most cases include \emph{DataDir}, i.e., the local directory to be used.
    \item[BackendClass] specifes which backend the Shepherd should use to communicate with the storage element service.
    \item[BackendCfg] specifies configuration parameters for the backend class: \textbf{StoreDir} and \textbf{TransferDir} are the directories the backend will use (see Section~\ref{sub:shepherd_implementation}), \textbf{TURLPrefix} is the URL of the storage element service ending with a `/'.
    \item[LibrarianURL] is the URL of a Librarian where the Shepherd should send the reports about the health of the stored files.
    \item[BartenderURL] is the URL of a Bartender to which the Shepherd should connect if it wants to offer a replica for replication or recover a corrupted replica.
\end{description}

@@

\begin{verbatim}
    <Service name="pythonservice" id="shepherd">
        <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
        <ServiceID>https://localhost:60000/Shepherd</ServiceID>
        <CheckPeriod>20</CheckPeriod>
        <MinCheckInterval>0.1</MinCheckInterval>
        <CreatingTimeout>600</CreatingTimeout>
        <StoreClass>storage.store.cachedpicklestore.CachedPickleStore</StoreClass>
        <StoreCfg>
            <DataDir>./shepherd_data1</DataDir>
        </StoreCfg>
        <BackendClass>storage.shepherd.hardlinkingbackend.HopiBackend</BackendClass>
        <BackendCfg>
            <StoreDir>./shepherd_store</StoreDir>
            <TransferDir>./shepherd_transfer</TransferDir>
            <TURLPrefix>https://localhost:60000/hopi/</TURLPrefix>
        </BackendCfg>
        <LibrarianURL>https://localhost:60000/Librarian</LibrarianURL>
        <BartenderURL>https://localhost:60000/Bartender</BartenderURL>
        <ClientSSLConfig FromFile="clientsslconfig.xml"/>
    </Service>    
\end{verbatim}
